---
title: "RMarkDownPlotly"
author: "Kara Schimmelfing"
date: "1/20/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

I chose to use the dataset mtcars for my plot to compare a variety of factors on the 1/4 mile time. 



## Slide with R Output

```{r cars, echo = FALSE, results='hide', message=FALSE, warning=FALSE}
library(plotly)
```
```{r plot}
p <- plot_ly(mtcars,x=~hp, y=~mpg, z=~wt,color=~qsec, mode= "markers",type = "scatter3d") %>% layout(title = "Horsepower, miles per gallon, weight and 1/4 mile time")
p
```
Please left-click and rotate the whole 3-dimension on any direction you want to view the visual.

## The End!



